Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-12 paper/main.tex
Added hashing time tables for all vectors

The numbers for uploading and downloading the 1GB file are summarized in
Tables \ref{tbl:hashingtimes:put1gb} and \ref{tbl:hashingtimes:get1gb}.
BLAKE, \ac{BMW}, Shabal and Simd outperforms \ac{SHA}-256 when both uploading
and downloading a 1GB file. The difference between the slowest (JH) and the
fastest (BLAKE) algorithm is 229.92s when uploading the one gigabyte file.

The third column in Tables \ref{tbl:hashingtimes:put1gb} and
\ref{tbl:hashingtimes:get1gb} contains the time spent doing other operations
than hashing, i.e. $Total time - Time spent hashing$. This number varies
between 227.37s and 252.66s during upload and 205.94s and 225.03s during
download. \emph{Fraction} displays the part of total time the calls to the
hashing libraries take.

\input{tables/hashingtimes}

>>>>

The numbers for uploading and downloading the different file vectors are
summarized in Tables \ref{tbl:hashingtimes:put1gb},
\ref{tbl:hashingtimes:get1gb}, \ref{tbl:hashingtimes:put100mb},
\ref{tbl:hashingtimes:get100mb}, \ref{tbl:hashingtimes:put1mb},
\ref{tbl:hashingtimes:get1mb}, \ref{tbl:hashingtimes:put1kb},
\ref{tbl:hashingtimes:get1kb}, \ref{tbl:hashingtimes:put1b} and
\ref{tbl:hashingtimes:get1b}.  The third column contains the time spent doing
other operations than hashing, i.e. \emph{Time spent not hashing = Total time -
Time spent hashing}. \emph{Fraction} displays the part of total time the calls
to the hashing libraries take.

As seen in Tables \ref{tbl:hashingtimes:put1gb} and
\ref{tbl:hashingtimes:get1gb}, Time spent not hashing varies between 227.37s and
252.66s during upload and 205.94s and 225.03s during download for a 1GB file.

BLAKE, \ac{BMW}, Shabal and Simd outperforms \ac{SHA}-256 when both uploading
and downloading a 1GB file. The difference between the slowest (JH) and the
fastest (BLAKE) algorithm is 229.92s when uploading the one gigabyte file.

\input{tables/hashingtimes_1gb}
\input{tables/hashingtimes_100mb}
\input{tables/hashingtimes_1mb}
\input{tables/hashingtimes_1kb}
\input{tables/hashingtimes_1b}
